### 2016-10-03 Chapters/ContinuumSolvationModels.tex
Always link acronyms back to list of acronyms

The molecular cavity is usually defined as a set of atom-centered
interlocking spheres. The radii are chosen from a suitable set, usually
van der Waals radii.\autocite{Bondi1964-dt, Mantina2009-hb}
If one imagines to model a solvent molecule as a rigid sphere,
three types of molecular surfaces can be defined:
\begin{enumerate}
  \item
    the union of the interlocking spheres surfaces is the \gls{vdWS},
    Figure \ref{fig:vdWS}
  \item the locus of points defined by the center of the solvent
    spherical probe while rolling over the \acrshort{vdWS} is the
    \gls{SAS}, Figure \ref{fig:SAS}
  \item the locus of points defined by the contact point of the solvent
    spherical probe while rolling over the \acrshort{vdWS} is the \gls{SES}, Figure \ref{fig:SES}.
\end{enumerate}
\begin{figure}[tb]
 \centering
 \begin{subfigure}{.45\textwidth}
   \centering
   \includegraphics[width=.85\textwidth]{vdWS.png}
   \caption{\acrlong*{vdWS} (\acrshort{vdWS})}
   \label{fig:vdWS}
 \end{subfigure}
 ~
 \begin{subfigure}{.45\textwidth}
   \centering
   \includegraphics[width=.85\textwidth]{SAS.png}
   \caption{\acrlong*{SAS} (\acrshort{SAS})}
   \label{fig:SAS}
 \end{subfigure}

 \begin{subfigure}{.45\textwidth}
   \centering
   \includegraphics[width=.85\textwidth]{SES.png}
   \caption{\acrlong*{SES} (\acrshort{SES})}
   \label{fig:SES}
 \end{subfigure}
 \caption{Molecular surfaces from interlocking sets of atom-centered spheres.
 Reproduced from \noparcite[ref.][]{Harbrecht2011-dk}.}
\end{figure}
Alternative definitions based on the isodensity surface of the molecular solute
have also been put forth.\autocite{Foresman1996-wv}

@@

As an example, let us consider the single-reference \acrshort{HF} and
\acrshort{KS}-\acrshort{DFT} methods introduced in Section
\ref{sec:mean-field}.
First of all, we need the appropriate \acrshort{SCF} energy functional
\emph{in vacuo}.
The \acrshort{AO} basis set expansion of the \glspl{MO} lets us define
the one-electron \acrshort{AO} density matrix as:
\begin{equation}
  D_{\mu\nu} = \sum_{i=1}^{N_O}C_{\mu i}C^\dagger_{\nu i}
\end{equation}
where $C_{\alpha r}$ are the \acrshort*{MO} expansion coefficients and
$N_O$ is the total number of occupied orbitals.
The \acrshort*{SCF} energy functional \emph{in vacuo} can now be
expressed as:
\begin{equation}\label{eq:scf-functional}
  \mathcal{E}(\mat{C}) \eqtr \mat{h}\mat{D} + \frac{1}{2}
  \mat{G}^\gamma(\mat{D})\mat{D} + E_\mathrm{xc}[\rho(\vect{r})] +
  V_\mathrm{NN},
\end{equation}
and has to be optimized under the \acrshort*{MO} orthonormality
constraint, easily introduced by means of Lagrangian multipliers:
\begin{equation}\label{eq:scf-lagrangian}
  \mathcal{L}(\mat{C}, \mat{\epsilon}) = \mathcal{E}(\mat{C}) -
  \sum_{ij}\epsilon_{ji}(\braket{\phi_i|\phi_j} - \delta_{ij})
\end{equation}
The various contributions are expressed in terms of \acrshort*{AO} basis
integral and density matrices:
\begin{subequations}
  \begin{align}
  h_{\mu\nu} = &= \int \diff\vect{r}
  \chi_\mu^\dagger(\vect{r})h(\vect{r})\chi_\nu(\vect{r}) \label{eq:ao-one-el} \\
  G_{\mu\nu}^\gamma &=
  \sum_{\kappa\lambda}D_{\kappa\lambda}(g_{\mu\nu\kappa\lambda} -
  \gamma g_{\mu\lambda\kappa\nu}) \label{eq:two-el-matrix} \\
  g_{\mu\nu\kappa\lambda} &=
  \int\diff\vect{r}\int\diff\vect{r}^\prime
  \Omega_{\mu\nu}(\vect{r}) g(\vect{r},\vect{r}^\prime)
  \Omega_{\kappa\lambda}(\vect{r}^\prime) \label{eq:ao-two-el} \\
  E_\mathrm{xc}[\rho(\vect{r})] &=
  \int\diff\vect{r}
  v_\mathrm{xc}(\vect{r})\Tr\mat{\Omega}(\vect{r})\mat{D} \label{eq:ao-xc} \\
  \Omega_{\mu\nu}(\vect{r}) &= \chi_\mu^\dagger(\vect{r})\chi_\nu(\vect{r}).
  \label{eq:ao-overlap}
  \end{align}
\end{subequations}
The quantum/classical polarizable \acrshort*{SCF} functional is obtained by adding the
polarization functional to Eq. \eqref{eq:scf-functional}:
\begin{equation}\label{eq:polarizable-scf-functional}
  \mathcal{L}_\mathrm{eff}(\mat{C}, \mat{\epsilon}, \s) =
  \mathcal{L}(\mat{C}, \mat{\epsilon}) +
  \frac{1}{2}{}^t\p\V\p + {}^t\p\Tr\mathbfup{s}\mat{D}.
\end{equation}
Differentiation with respect to the variational degrees of freedom
yields the \acrshort*{KS} and polarization equations:
\begin{subequations}
  \begin{align}
    \mat{F}\mat{C} &= \mat{S}\mat{C}\mat{\epsilon} \\
    \V\p &+ \Tr\mathbfup{s}\mat{D} = 0 \label{eq:polarization-stat}
  \end{align}
\end{subequations}
The \acrshort*{KS} matrix now includes environment contributions:
\begin{equation}
  f_{\mu\nu} = h_{\mu\nu}  + G^\gamma_{\mu\nu}(\mat{D}) + f_{\mathrm{xc};\mu\nu}
  + {}^t\p\s_{\mu\nu}.
\end{equation}
With respect to the coupling described in abstract terms above, the
\acrshort*{SCF} case is formally simpler. In fact, whereas in the
general case the source term depends on \emph{both} primal (amplitudes)
and dual (multipliers) variational degrees of freedom, here only the
dependence on the primal parameters (\acrshort*{MO} coefficients) needs
to be considered.\autocite{Lipparini2011-aj}

>>>>

The molecular cavity is usually defined as a set of atom-centered
interlocking spheres. The radii are chosen from a suitable set, usually
van der Waals radii.\autocite{Bondi1964-dt, Mantina2009-hb}
If one imagines to model a solvent molecule as a rigid sphere,
three types of molecular surfaces can be defined:
\begin{enumerate}
  \item
    the union of the interlocking spheres surfaces is the \gls{vdWS},
    Figure \ref{fig:vdWS}
  \item the locus of points defined by the center of the solvent
    spherical probe while rolling over the \acrshort{vdWS} is the
    \gls{SAS}, Figure \ref{fig:SAS}
  \item the locus of points defined by the contact point of the solvent
    spherical probe while rolling over the \acrshort{vdWS} is the \gls{SES}, Figure \ref{fig:SES}.
\end{enumerate}
\begin{figure}[tb]
 \centering
 \begin{subfigure}{.45\textwidth}
   \centering
   \includegraphics[width=.85\textwidth]{vdWS.png}
   \caption{\acrlong{vdWS} (\acrshort{vdWS})}
   \label{fig:vdWS}
 \end{subfigure}
 ~
 \begin{subfigure}{.45\textwidth}
   \centering
   \includegraphics[width=.85\textwidth]{SAS.png}
   \caption{\acrlong{SAS} (\acrshort{SAS})}
   \label{fig:SAS}
 \end{subfigure}

 \begin{subfigure}{.45\textwidth}
   \centering
   \includegraphics[width=.85\textwidth]{SES.png}
   \caption{\acrlong{SES} (\acrshort{SES})}
   \label{fig:SES}
 \end{subfigure}
 \caption{Molecular surfaces from interlocking sets of atom-centered spheres.
 Reproduced from \noparcite[ref.][]{Harbrecht2011-dk}.}
\end{figure}
Alternative definitions based on the isodensity surface of the molecular solute
have also been put forth.\autocite{Foresman1996-wv}

@@

As an example, let us consider the single-reference \acrshort{HF} and
\acrshort{KS}-\acrshort{DFT} methods introduced in Section
\ref{sec:mean-field}.
First of all, we need the appropriate \acrshort{SCF} energy functional
\emph{in vacuo}.
The \acrshort{AO} basis set expansion of the \glspl{MO} lets us define
the one-electron \acrshort{AO} density matrix as:
\begin{equation}
  D_{\mu\nu} = \sum_{i=1}^{N_O}C_{\mu i}C^\dagger_{\nu i}
\end{equation}
where $C_{\alpha r}$ are the \acrshort{MO} expansion coefficients and
$N_O$ is the total number of occupied orbitals.
The \acrshort{SCF} energy functional \emph{in vacuo} can now be
expressed as:
\begin{equation}\label{eq:scf-functional}
  \mathcal{E}(\mat{C}) \eqtr \mat{h}\mat{D} + \frac{1}{2}
  \mat{G}^\gamma(\mat{D})\mat{D} + E_\mathrm{xc}[\rho(\vect{r})] +
  V_\mathrm{NN},
\end{equation}
and has to be optimized under the \acrshort{MO} orthonormality
constraint, easily introduced by means of Lagrangian multipliers:
\begin{equation}\label{eq:scf-lagrangian}
  \mathcal{L}(\mat{C}, \mat{\epsilon}) = \mathcal{E}(\mat{C}) -
  \sum_{ij}\epsilon_{ji}(\braket{\phi_i|\phi_j} - \delta_{ij})
\end{equation}
The various contributions are expressed in terms of \acrshort{AO} basis
integral and density matrices:
\begin{subequations}
  \begin{align}
  h_{\mu\nu} = &= \int \diff\vect{r}
  \chi_\mu^\dagger(\vect{r})h(\vect{r})\chi_\nu(\vect{r}) \label{eq:ao-one-el} \\
  G_{\mu\nu}^\gamma &=
  \sum_{\kappa\lambda}D_{\kappa\lambda}(g_{\mu\nu\kappa\lambda} -
  \gamma g_{\mu\lambda\kappa\nu}) \label{eq:two-el-matrix} \\
  g_{\mu\nu\kappa\lambda} &=
  \int\diff\vect{r}\int\diff\vect{r}^\prime
  \Omega_{\mu\nu}(\vect{r}) g(\vect{r},\vect{r}^\prime)
  \Omega_{\kappa\lambda}(\vect{r}^\prime) \label{eq:ao-two-el} \\
  E_\mathrm{xc}[\rho(\vect{r})] &=
  \int\diff\vect{r}
  v_\mathrm{xc}(\vect{r})\Tr\mat{\Omega}(\vect{r})\mat{D} \label{eq:ao-xc} \\
  \Omega_{\mu\nu}(\vect{r}) &= \chi_\mu^\dagger(\vect{r})\chi_\nu(\vect{r}).
  \label{eq:ao-overlap}
  \end{align}
\end{subequations}
The quantum/classical polarizable \acrshort{SCF} functional is obtained by adding the
polarization functional to Eq. \eqref{eq:scf-functional}:
\begin{equation}\label{eq:polarizable-scf-functional}
  \mathcal{L}_\mathrm{eff}(\mat{C}, \mat{\epsilon}, \s) =
  \mathcal{L}(\mat{C}, \mat{\epsilon}) +
  \frac{1}{2}{}^t\p\V\p + {}^t\p\Tr\mathbfup{s}\mat{D}.
\end{equation}
Differentiation with respect to the variational degrees of freedom
yields the \acrshort{KS} and polarization equations:
\begin{subequations}
  \begin{align}
    \mat{F}\mat{C} &= \mat{S}\mat{C}\mat{\epsilon} \\
    \V\p &+ \Tr\mathbfup{s}\mat{D} = 0 \label{eq:polarization-stat}
  \end{align}
\end{subequations}
The \acrshort{KS} matrix now includes environment contributions:
\begin{equation}
  f_{\mu\nu} = h_{\mu\nu}  + G^\gamma_{\mu\nu}(\mat{D}) + f_{\mathrm{xc};\mu\nu}
  + {}^t\p\s_{\mu\nu}.
\end{equation}
With respect to the coupling described in abstract terms above, the
\acrshort{SCF} case is formally simpler. In fact, whereas in the
general case the source term depends on \emph{both} primal (amplitudes)
and dual (multipliers) variational degrees of freedom, here only the
dependence on the primal parameters (\acrshort{MO} coefficients) needs
to be considered.\autocite{Lipparini2011-aj}

### 2016-10-03 Chapters/ContributionsSummary.tex
Always link acronyms back to list of acronyms

\pcmsolver currently offers an implementation of the traditional collocation
solvers for isotropic media,\autocite{Tomasi2005-vm}
together with some unique functionalities: the wavelet Galerkin solvers on smooth
molecular surfaces,\autocite{Weijo2010-hy, Bugeanu2015-tp} the Green’s
functions for spherical diffuse interfaces\autocite{DiRemigio2016-nn} and
the delayed solvers for real-time \acrlong*{TDSCF}
simulations.\autocite{Corni2015-pe}

>>>>

\pcmsolver currently offers an implementation of the traditional collocation
solvers for isotropic media,\autocite{Tomasi2005-vm}
together with some unique functionalities: the wavelet Galerkin solvers on smooth
molecular surfaces,\autocite{Weijo2010-hy, Bugeanu2015-tp} the Green’s
functions for spherical diffuse interfaces\autocite{DiRemigio2016-nn} and
the delayed solvers for real-time \acrlong{TDSCF}
simulations.\autocite{Corni2015-pe}

### 2016-10-03 Chapters/MathematicalResults.tex
Always link acronyms back to list of acronyms

The \acrshort*{CCSD} Lagrangian is then:
\begin{equation}\label{eq:ccsd-lagrangian}
 \begin{aligned}
 \mathcal{L}(\tamp{}, \tbar{})_\mathrm{CCSD}
&=
 E_0
 + \sum_{u=1}^{2}\tbar{\mu_u}\denom{\mu_u}\tamp{\mu_u}
 + \braket{\mathrm{HF} | \check{\Phi} + \commutator{\check{\Phi}}{T_2} | \mathrm{HF}} \\
 &+ \braket{\tbar{1} | \check{\Phi} + \commutator{\check{\Phi}}{T_2} | \mathrm{HF}} \\
 &+ \braket{\tbar{2} | \check{\Phi} + \commutator{\check{\Phi}}{T_2}
   +\frac{1}{2}\commutator{\commutator{\check{\Phi}}{T_2}}{T_2} | \mathrm{HF}}
  \end{aligned}
\end{equation}
with the governing equations:
\begin{subequations}\label{eq:ccsd-equations}
  \begin{align}
   \denom{\mu_1}\tamp{\mu_1} &+ \braket{\mu_1 | \check{\Phi} + \commutator{\check{\Phi}}{T_2} | \mathrm{HF}}
             = 0 \label{eq:ccsd-singles-amplitudes}\\
   \denom{\mu_2}\tamp{\mu_2} &+
   \braket{\mu_2 | \check{\Phi} + \commutator{\check{\Phi}}{T_2} +\frac{1}{2}\commutator{\commutator{\check{\Phi}}{T_2}}{T_2} | \mathrm{HF}}
             = 0 \label{eq:ccsd-doubles-amplitudes}\\
    \denom{\mu_1}\tbar{\mu_1} &+
    \braket{\mathrm{HF} | \commutator{\check{\Phi}}{\cluster{\mu_1}} | \mathrm{HF}} +
    \braket{\tbar{1} |
      \commutator{\check{\Phi}}{\cluster{\mu_1}}
    + \commutator{\commutator{\check{\Phi}}{\cluster{\mu_1}}}{T_2}
    | \mathrm{HF}} \nonumber \\
   &+ \braket{\tbar{2} |
      \commutator{\check{\Phi}}{\cluster{\mu_1}}
    + \commutator{\commutator{\check{\Phi}}{\cluster{\mu_1}}}{T_2}
    | \mathrm{HF}}
             = 0 \label{eq:ccsd-singles-multipliers} \\
    \denom{\mu_2}\tbar{\mu_2} &+
    \braket{\mathrm{HF} | \commutator{\check{\Phi}}{\cluster{\mu_2}} | \mathrm{HF}} +
    \braket{\tbar{1} |
      \commutator{\check{\Phi}}{\cluster{\mu_2}}
    | \mathrm{HF}} \nonumber \\
   &+ \braket{\tbar{2} |
      \commutator{\check{\Phi}}{\cluster{\mu_2}}
    + \commutator{\commutator{\check{\Phi}}{\cluster{\mu_2}}}{T_2}
    | \mathrm{HF}}
             = 0 \label{eq:ccsd-doubles-multipliers}
  \end{align}
\end{subequations}
Equations \eqref{eq:ccsd-doubles-amplitudes},
\eqref{eq:ccsd-singles-multipliers} and \eqref{eq:ccsd-doubles-multipliers} can
be compared with the corresponding \acrshort{CC2} equations
\eqref{eq:cc2-doubles-amplitudes}, \eqref{eq:cc2-singles-multipliers} and
\eqref{eq:cc2-doubles-multipliers}, respectively, to highlight which terms were neglected in
constructing the iterative method for the approximate inclusion of double excitations.

@@

This is a consequence of the well-known fact that the \acrshort*{CC} energy can

@@

The use of normal-ordered operators is common in \acrlong*{CC} theory. Both for
the dressed and bare representations, the expectation values of such operators
can be formed by simply replacing the operator with its normal-ordered counterpart,
$\check{O}_\mathrm{N}$ or $O$, respectively.
This achieves elimination of the reference expectation value from the first
term in equation \eqref{eq:ccs-expectation-value}.

@@

We introduce the following auxiliary potential:
\begin{subequations}
\begin{empheq}[left={h(\vect{r}) = \empheqlbrace}]{align}
    &\int_{\mathbb{R}^3}\Gi\rhoi(\vect{r}^\prime)\diff \vect{r}^\prime  \quad \vect{r} \in \Omegai \\
    &\int_{\mathbb{R}^3}\Ge\rhoi(\vect{r}^\prime)\diff \vect{r}^\prime  \quad \vect{r} \in \Omegae
\end{empheq}
\end{subequations}
for which we have:
\begin{subequations}
\begin{empheq}[left={\empheqlbrace}]{align}
    \nabla^2 h &= \rhoi \,\, \text{in}\,\, \Omegai \\
    \Le h &= 0 \,\, \text{in}\,\, \Omegae
\end{empheq}
\end{subequations}
We then define the \emph{reaction potential} as:
\begin{equation}
  \xi = u - h
\end{equation}
such that:
\begin{subequations}
  \begin{align}[left={\empheqlbrace}]
  \nabla^2 \xi &= 0 \,\, \text{in}\,\, \Omegai \\
  \Le \xi &= 0 \,\, \text{in}\,\, \Omegae \\
  -[\xi] &= [h] \,\, \text{on}\,\, \Gamma \\
  -[\partial_L \xi] &= [\partial_L h] \,\, \text{on}\,\, \Gamma
\end{align}
\end{subequations}
inside the cavity, the reaction potential can be represented by a
\emph{single layer potential}:
\begin{equation}
  \xi_\mathrm{i} = \bi{S}_\mathrm{i}\sigma
\end{equation}
where the function $\sigma$ is the, yet unknown, \acrlong*{ASC}.

>>>>

The \acrshort{CCSD} Lagrangian is then:
\begin{equation}\label{eq:ccsd-lagrangian}
 \begin{aligned}
 \mathcal{L}(\tamp{}, \tbar{})_\mathrm{CCSD}
&=
 E_0
 + \sum_{u=1}^{2}\tbar{\mu_u}\denom{\mu_u}\tamp{\mu_u}
 + \braket{\mathrm{HF} | \check{\Phi} + \commutator{\check{\Phi}}{T_2} | \mathrm{HF}} \\
 &+ \braket{\tbar{1} | \check{\Phi} + \commutator{\check{\Phi}}{T_2} | \mathrm{HF}} \\
 &+ \braket{\tbar{2} | \check{\Phi} + \commutator{\check{\Phi}}{T_2}
   +\frac{1}{2}\commutator{\commutator{\check{\Phi}}{T_2}}{T_2} | \mathrm{HF}}
  \end{aligned}
\end{equation}
with the governing equations:
\begin{subequations}\label{eq:ccsd-equations}
  \begin{align}
   \denom{\mu_1}\tamp{\mu_1} &+ \braket{\mu_1 | \check{\Phi} + \commutator{\check{\Phi}}{T_2} | \mathrm{HF}}
             = 0 \label{eq:ccsd-singles-amplitudes}\\
   \denom{\mu_2}\tamp{\mu_2} &+
   \braket{\mu_2 | \check{\Phi} + \commutator{\check{\Phi}}{T_2} +\frac{1}{2}\commutator{\commutator{\check{\Phi}}{T_2}}{T_2} | \mathrm{HF}}
             = 0 \label{eq:ccsd-doubles-amplitudes}\\
    \denom{\mu_1}\tbar{\mu_1} &+
    \braket{\mathrm{HF} | \commutator{\check{\Phi}}{\cluster{\mu_1}} | \mathrm{HF}} +
    \braket{\tbar{1} |
      \commutator{\check{\Phi}}{\cluster{\mu_1}}
    + \commutator{\commutator{\check{\Phi}}{\cluster{\mu_1}}}{T_2}
    | \mathrm{HF}} \nonumber \\
   &+ \braket{\tbar{2} |
      \commutator{\check{\Phi}}{\cluster{\mu_1}}
    + \commutator{\commutator{\check{\Phi}}{\cluster{\mu_1}}}{T_2}
    | \mathrm{HF}}
             = 0 \label{eq:ccsd-singles-multipliers} \\
    \denom{\mu_2}\tbar{\mu_2} &+
    \braket{\mathrm{HF} | \commutator{\check{\Phi}}{\cluster{\mu_2}} | \mathrm{HF}} +
    \braket{\tbar{1} |
      \commutator{\check{\Phi}}{\cluster{\mu_2}}
    | \mathrm{HF}} \nonumber \\
   &+ \braket{\tbar{2} |
      \commutator{\check{\Phi}}{\cluster{\mu_2}}
    + \commutator{\commutator{\check{\Phi}}{\cluster{\mu_2}}}{T_2}
    | \mathrm{HF}}
             = 0 \label{eq:ccsd-doubles-multipliers}
  \end{align}
\end{subequations}
Equations \eqref{eq:ccsd-doubles-amplitudes},
\eqref{eq:ccsd-singles-multipliers} and \eqref{eq:ccsd-doubles-multipliers} can
be compared with the corresponding \acrshort{CC2} equations
\eqref{eq:cc2-doubles-amplitudes}, \eqref{eq:cc2-singles-multipliers} and
\eqref{eq:cc2-doubles-multipliers}, respectively, to highlight which terms were neglected in
constructing the iterative method for the approximate inclusion of double excitations.

@@

This is a consequence of the well-known fact that the \acrshort{CC} energy can

@@

The use of normal-ordered operators is common in \acrlong{CC} theory. Both for
the dressed and bare representations, the expectation values of such operators
can be formed by simply replacing the operator with its normal-ordered counterpart,
$\check{O}_\mathrm{N}$ or $O$, respectively.
This achieves elimination of the reference expectation value from the first
term in equation \eqref{eq:ccs-expectation-value}.

@@

We introduce the following auxiliary potential:
\begin{subequations}
\begin{empheq}[left={h(\vect{r}) = \empheqlbrace}]{align}
    &\int_{\mathbb{R}^3}\Gi\rhoi(\vect{r}^\prime)\diff \vect{r}^\prime  \quad \vect{r} \in \Omegai \\
    &\int_{\mathbb{R}^3}\Ge\rhoi(\vect{r}^\prime)\diff \vect{r}^\prime  \quad \vect{r} \in \Omegae
\end{empheq}
\end{subequations}
for which we have:
\begin{subequations}
\begin{empheq}[left={\empheqlbrace}]{align}
    \nabla^2 h &= \rhoi \,\, \text{in}\,\, \Omegai \\
    \Le h &= 0 \,\, \text{in}\,\, \Omegae
\end{empheq}
\end{subequations}
We then define the \emph{reaction potential} as:
\begin{equation}
  \xi = u - h
\end{equation}
such that:
\begin{subequations}
  \begin{align}[left={\empheqlbrace}]
  \nabla^2 \xi &= 0 \,\, \text{in}\,\, \Omegai \\
  \Le \xi &= 0 \,\, \text{in}\,\, \Omegae \\
  -[\xi] &= [h] \,\, \text{on}\,\, \Gamma \\
  -[\partial_L \xi] &= [\partial_L h] \,\, \text{on}\,\, \Gamma
\end{align}
\end{subequations}
inside the cavity, the reaction potential can be represented by a
\emph{single layer potential}:
\begin{equation}
  \xi_\mathrm{i} = \bi{S}_\mathrm{i}\sigma
\end{equation}
where the function $\sigma$ is the, yet unknown, \acrlong{ASC}.
